\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-15 paper/mswp2012-proposal.tex

Studies\footnote{\url{http://www.sueddeutsche.de/gesundheit/gesundheitsbericht-des-rki-fast-ein-viertel-der-deutschen-ist-fettleibig-1.1382763}} show, that about 23 Percent of the people in Germany are obese nowadays. Being overweight not only affects your attractiveness, it can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.  \\

>>>>

Studies\citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays. Being overweight not only affects your attractiveness, it can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.  \\
